---
title: "Wonderful html world of RMarkdown"
output:
  html_document
---

<style type="text/css">
body{ /* Normal  */
  font-size: 14px;
}
td {  /* Table  */
   font-size: 12px;
}
h1 { /* Header 1 */
 font-size: 24px;
 color: darkBlue;
}
h2 { /* Header 2 */
 font-size: 20px;
 color: darkBlue;
}
h3 { /* Header 3 */
 font-size: 18px;
 color: darkBlue;
}
h4 { /* Header 4 */
 font-size: 16px;
 color: darkBlue;
}
code.r{ /* Code block */
  font-size: 12px;
  white-space:pre !important;
  overflow-x:scroll !important;
  word-break: keep-all !important;
  word-wrap: initial !important;
}
pre { /* Code block */
  font-size: 12px;
  white-space:pre !important;
  overflow-x:scroll !important;
  word-break: keep-all !important;
  word-wrap: initial !important;
}

</style>

# Przykład

```{r}
set.seed(15390)

x <- 1L:5
y <- 1L:5

plot(x, y)
```


# Tabele {.tabset}

## Normalna tabela

```{r}
iris
```

## Elegancka tabela

```{r}
library(DT)

datatable(iris, extensions = 'Buttons', 
          filter = "top", rownames = FALSE, #style = "bootstrap",
          options = list(dom = "Brtip",
                         buttons = c("copy", "csv", "excel", "print")))

```
